Freezing of a Weeks-Chandler-Anderson Fluid using Classical Density Functional Theory

### 2021-01-10 papers/thesis-kirstie/thesis.tex
edits

\textcolor{blue}{

@@

written as

@@

@@

                 &+ \color{white}\left[\color{blue}\left(\int n\delta(r-R) d\vec r\right)\left(\int n\frac{\delta(r-R)}{4\pi R} d\vec r \right) \right]\color{blue}V   \\          

@@

which are added for the relation to be satisfied, 

@@

                &+ \color{white}\left(\color{blue}\int w_1(\vec u - \vec r_i)w_2(\vec u - \vec r_j) d\vec x ~-\int \vec {w}_1(\vec u - \vec r_i)\cdot\vec {w}_2(\vec u - \vec r_j) d\vec u\right)    \\

@@

                &+ \color{white}\left[\color{blue} \int n(\vec r_i) \vec {w}_1(\vec u - \vec r_i)~d\vec r_i \cdot \int n(\vec r_j) \vec {w}_2(\vec u - \vec r_j)~d\vec r_j \right]\color{blue}d\vec u  \\

@@

                &\text{or replacing u notation with r} \nonumber \\
                &= k_BT\int \Phi(\{n_\alpha(\vec r)\})~d\vec r             

@@

    n_\alpha(\vec r)=\int n(\vec r')w_\alpha(\vec r-\vec r')~d\vec r'  

@@

}\textcolor{blue}{
Lifting the restriction to the low density limit, Rosenfeld derived an
expression for the excess Helmholtz free energy by noting that the higher
order terms in the virial expansion can all be written in terms of an 
"exclusion volume" which is given by Equation~\ref{exclusion-volume}, 
and an "overlap volume".
The exclusion volume is the spherical volume about the center of one sphere 
which the center of another sphere can not enter, and is used to describe
terms with $f_{ij}=f(|\vec r_i - \vec r_j|)$ as has been seen. The overlap volume is 
the volume of intersection between two spheres that overlap, and is used in conjunction 
with the exclusion volume to describe higher order terms in the expansion~\cite{rosenfeld1988}. 
The resulting expression for the excess Helmholtz free energy is given in 
Equation~\ref{FexfromSPT} with $\Phi$'s defined in Equations~\ref{Phi1equation} 
through~\ref{oldPhi3equation}, and
and weighted densities defined in Equation~\ref{weighted-density}, 
and reduces to the same result obtained from Scaled Particle Theory for a 
homogeneous hard-sphere fluid. 
}
%In order to apply classical Density Functional Theory to a system that has
%a fixed temperature, volume, and number of particles, a functional for 
%the Helmholtz free energy must first be formed. An expression for the ideal 
%portion of the Helmholtz free energy is given by Equation~\ref{eq:Fideal-n(r)}, 
%but forming an expression for the excess Helmholtz free
%energy from Equation~\ref{eq:Fexcess-simplified} for the particular fluid 
%being modeled can be challenging. 
%Soft Fundamental Measure Theory (SFMT) is a method for forming an 
%expression for the excess Helmholtz free energy of a soft-sphere fluid
%that does not depend on explicitly taking into account the interaction 
%that each sphere with every other sphere in the fluid (as required by 
%Equation~\ref{eq:Fexcess-simplified}). In the next chapter on methods, we
%will use an SFMT functional that we adapt to fit the soft-sphere WCA fluid.
%SFMT was developed by Schmidt~\cite{schmidt1999density, schmidt2000fluid} 
%for soft-spheres. It is an extension of Fundamental Measure Theory (FMT) 
%originally developed by 
%Rosenfeld~\cite{rosenfeld1989, rosenfeld1994, rosenfeld1996, fmtfromsptandsignerror} 
%for the hard-sphere fluid, and which expanded 
%Scaled Particle Theory (SPT)~\cite{santos2012phi3} 
%to inhomogeneous, or non-uniform hard-sphere fluids.

Scaled Particle Theory
seeks a general expression for the excess chemical 
potential of a homogeneous hard-sphere fluid which can then be integrated 
to find the excess Helmholtz free energy according to the relation
\begin{equation}\mu_{ex}=\frac{\partial{F_{ex}}}{\partial{N}}\bigg|_{T,V}{~~~~~}\rightarrow{~~~~~}F_{ex}=\int{\mu_{ex}dN}\end{equation}
It is an extension of the work done by Widom who showed that the excess 
chemical potential of a homogeneous fluid corresponds to the reversible 
work of inserting a sphere of radius R into a fluid consisting of hard 
spheres of radius R. 
\begin{align}
	\mu_{ex}=W_{rev}(R){~~~~}\text{work to insert a hard sphere of radius R}
\end{align}
Widom's result was obtained by considering the difference 
in the excess Helmholtz free energy when one atom is added to an otherwise 
closed system. He showed that the excess chemical potential is related to 
the ensemble average of the Boltzman factor for the potential energy 
difference $V_{diff}$ between a system with N atoms and one with N+1 atoms. 
The resulting equation, shown below, is known as Widom's Insertion 
Formula~\cite{Hansen}.
\begin{align} \label{mu-der-int}
    \mu_{ex}=\frac{F_{ex}(N+1)-F_{ex}(N)}{\Delta{N}}\bigg|_{T,V}
\end{align}
\begin{equation}\label{widoms-insertion-formula}{~}=-k_BT\ln\left(<e^{-\beta{V_{diff}}}>\right)\end{equation}
where 
\begin{align}
    <e^{-\beta{V_{diff}}}>=\sum_s{P_se^{-\beta V_s}}
\end{align}
and
\begin{align}
    Z=\sum_s{e^{-\beta V_s}}
\end{align}

The quantity $<e^{-\beta{V_{diff}}}>$ can be evaluated by considering that
there will be a change in the potential energy of $V_{diff}$ if one sphere
is added, but no change in potential energy if no sphere is added ($V_{diff}=0$). 
In this case, $P_s=\frac{e^{-\beta V_s}}{Z}$.
%at each point in the fluid, there is a probability that 
%a hard sphere of radius R has space available to exist at that point
%without overlapping with other spheres, or it does not, as shown in 
Widom's Insertion formula Equation~\ref{widoms-insertion-formula}, 
then becomes~\cite{Hansen}
\begin{align} 
	\mu_{ex} &= -k_BT\ln\left(e^{-\beta{V_{diff}}}+1\right)  \\
	         &= V_{diff} \\
             &= W_{rev}(R)  \label{workrev}
\end{align}
\begin{figure}
    \centering
    \includegraphics[height=7cm]{figs/P_overlap.pdf}
    \caption{No energy is needed to place a sphere at a position where 
    there is no overlap, such as that shown by the black dot near the 
    top. But it is not possible to place a sphere at a position where 
    an overlap occurs.}
    \label{fig:p_overlap}
  \end{figure}
The quantity $<e^{-\beta{V_{diff}}}>$ can also be evaluated by considering
that it takes no energy for a hard sphere to be placed at a point
in the fluid where it does not overlap with any other spheres 
($V_{diff}=0$), but it would require infinite energy ($V_{diff}=\infty$)
to place a sphere where it would overlap another sphere, as described 
in Figure~\ref{fig:p_overlap}. 
In this case Equation~\ref{widoms-insertion-formula} becomes~\cite{Hansen}
\begin{align} \label{muexcess}
  \mu_{excess}(R_{cavity}=R)=-k_BT\ln(1-n\frac{4\pi}{3}R^3) 
\end{align}
where the radius of the cavity $R_{cavity}$ equals the radius of a 
hard sphere R, and $nV_{Sphere}$, which is equal to the total volume 
occupied by the spheres divided by the total volume available, 
is the probability that a sphere cannot be placed at some random
point in the homogeneous fluid of number density, $n$, without
overlapping with another sphere. $P_s$ would then have values of
$nV_{Sphere}$ and $1-nV_{Sphere}$.
Combining  Equations~\ref{workrev} 
and \ref{muexcess} gives
\begin{align}
  %W_{rev}(R_{cavity}=R)=-k_BT\ln(1-n\frac{4\pi}{3}R^3)
  W_{rev}(R_{cavity}=R)=-k_BT\ln(1-\eta) 
\end{align}
where $\eta$ is the packing fraction defined as
\begin{equation}{\eta = \frac{\mbox{Volume occupied by the spheres}}{\mbox{Total Volume}}}\end{equation}
\begin{equation}{\eta = \frac{N\frac{4}{3}\pi{R^3}}{V}}\end{equation}

Scaled Particle Theory forms a more general result for the reversible work 
as a function of the radius of the cavity by considering additional 
cases where the cavity is larger, and much larger than the radius of 
a hard sphere, and requiring continuity of the functions for the 
different cases and their derivatives (first and second). 
By setting the radius of the cavity to the hard sphere radius, the 
more general work equation becomes equal to the chemical potential. 
Details of this procedure can be found 
in Theory of Simple Fluids by Hansen and McDonald~\cite{Hansen}.  
An expression for the excess Helmholtz free energy in terms of the
packing fraction $\eta$ can then be obtained through 
Equation~\ref{mu-der-int}. 
%
%By requiring continuity of the functions valid for different cavity 
%sizes, along with their first and second derivatives, an equation for 
%the work is obtained which can then be used to form 
%set equal to the excess chemical 
%potential by setting the cavity radius to the radius of hard sphere. 
%
%Forming a more general result by requiring continuity of the functions, 
%along with their first and second derivatives, for the reversible work
%written for fluids with a cavity radius equal to, larger than, or very 
%much larger than the hard sphere radius R, 
%
%Scaled Particle Theory arrives at 
%an expression for the excess Helmholtz free energy of 
%a homogeneous hard-sphere fluid in terms of the packing fraction $\eta$.
%For details, see Theory of Simple Fluids by Hansen and McDonald~\cite{Hansen}. 
\begin{align}\label{Fexcess-SPT}
    F_{excess}=k_BT\left(-ln(1-\eta)+\frac{3\eta}{1-\eta}+\frac{3{\eta}^2}{2(1-\eta)^2}\right)N
\end{align}

Fundamental Measure Theory can be constructed from Equation~\ref{Fexcess-SPT}  
%and provides an expression for the excess Helmholtz free energy of an 
%inhomogeneous 
%hard-sphere fluid as a functional of the number density profile $n(\vec r)$. 
%
%Soft Fundamental Measure Theory (SFMT), which will be used in this paper, 
%is an extension of FMT and provides an expression for the excess Helmholtz
%free energy of fluids with soft potentials like that of the WCA fluid. 
%It will be helpful to continue looking at FMT before addressing SFMT.
%FMT begins 
by noticing that a quantity $G_{3}$ can be defined such that
\begin{equation}{\eta =\left(\frac{N}{V}\right)\frac{4}{3}\pi{R^3}=nG_{3}}\end{equation}
where $G_{3}$ is the volume of a sphere. 
Likewise, by defining quantities
\begin{equation}{G_{2}=4\pi{R^2}}\end{equation}
\begin{equation}{G_{1}=R}\end{equation}
\begin{equation}{G_{0}=1}\end{equation}
where $G_{2}$ is the surface area of a sphere, and $G_{1}$ is the 
radius of a sphere, Equation~\ref{Fexcess-SPT} can be written as
\begin{equation}\label{FexfromSPTinthermsofG}{F_{excess}=k_{B}T\left(-nG_{0}ln(1-nG_{3})+\frac{nG_{1}nG_{2}}{1-nG_{3}}+\frac{nG_{2}^3}{24\pi(1-Gn_{3})^2}\right)V}\end{equation}
The quantities $G_{3}, G_{2}, G_{1},$ and $G_{0}$ are fundamental 
geometric measures of a sphere, and are what give rise to the name
Fundamental Measure Theory. Introducing a set of variables
%weighted densities $n_{i}=nG_{i}$ 
given by
\begin{equation}\label{n3}{n_{3}=nG_{3}=\left(\frac{N}{V}\right)\frac{4}{3}\pi{R^3}=\eta}\end{equation}
\begin{equation}\label{n2}{n_{2}=nG_{2}=\left(\frac{N}{V}\right)4\pi{R^2}=\frac{3\eta}{R}}\end{equation}
\begin{equation}\label{n1}{n_{1}=nG_{1}=\left(\frac{N}{V}\right)R}\end{equation}
\begin{equation}\label{n0}{n_{0}=nG_{0}=\left(\frac{N}{V}\right)}\end{equation}
Equation~\ref{FexfromSPTinthermsofG} can be written as
\begin{align}\label{FexfromSPT}
    F_{excess}=k_{B}T\left(-n_{0}ln(1-n_{3})+\frac{n_{1}n_{2}}{1-n_{3}}+\frac{n_{2}^3}{24\pi(1-n_{3})^2}\right)V
\end{align}
which has the form 
\begin{align}
    F_{excess} = k_BT(\Phi_1+\Phi_2+\Phi_3)V
\end{align}
%where 
\begin{align}
   \Phi_1 &= -n_{0}\ln(1-n_{3}) \label{Phi1equation} \\
   \Phi_2 &= \frac{n_{1}n_{2}}{1-n_{3}} \\
   \Phi_3 &= \frac{n_{2}^3}{24\pi(1-n_{3})^2}   \label{oldPhi3equation}
\end{align}

The quantities $n_{0},n_{1},n_{2},n_{3}$ can be considered as weighted 
densities where the weights are given by $G_{0},G_{1},G_{2},G_{3}$ respectively.
\begin{align}
    n_{i}=nG_{i}
\end{align}
These weights are valid for determining the excess free energy of a system of 
hard spheres with a homogeneous number density n. But these weights, and 
their related  weighted densities, can be written in a more general form 
allowing for their extension to a system with a spatially varying number 
density $n(\vec{r})$, that is, an inhomogeneous fluid, in which case, the
excess Helmholtz free energy is written as
\begin{equation}\label{eq:F_ex-n-of-r}{F_{excess}[n(\vec{r})]= k_BT\int(\Phi_1(\vec{r})+\Phi_2(\vec{r})+\Phi_3(\vec{r}{)) d}\vec{r}}\end{equation} 
Using a backwards Heaviside step function defined as
\begin{equation}{\Theta(|\vec{r}|-R)=\left\{ \begin{array}{rc} 1 & 0<r \leq R \\ 0  & r>R \end{array}\right.}\end{equation}
the following expressions are obtained
\begin{equation}{G_{3}=\int_{Volume}{\Theta(|\vec{r}|-R)d{\vec{r}}} = \frac{4}{3}\pi{R^3}}\end{equation}
\begin{equation}{G_{2}=\int_{Volume}{\delta(|\vec{r}|-R)d{\vec{r}}} = 4\pi{R^2}}\end{equation}
\begin{equation}{G_{1}=\int_{Volume}{\frac{\delta(|\vec{r}|-R)}{r}d{\vec{r}}} = R}\end{equation}
\begin{equation}{G_{0}=\int_{Volume}{\frac{\delta(|\vec{r}|-R)}{r^2}d{\vec{r}}} = 1}\end{equation}
where the weighted densities can now be expressed as
\begin{align}
    n_{i}=\int_{Volume}{nw_{i}(r)}d{\vec{r}}
\end{align} 
or for a spatially varying number density $n(\vec{r})$,
\begin{equation}\label{weighted-density}{n_i(\vec{r})=\int_{Volume}{n(\vec{r'})w_i(|\vec{r}-\vec{r'}|)d{\vec{r'}}}}\end{equation}
with weight functions
\begin{equation}\label{eq:w3}{w_{3}=\Theta(|\vec{r}|-R)}\end{equation}
\begin{equation}\label{eq:w2}{w_{2}=\delta(|\vec{r}|-R)}\end{equation}
\begin{equation}\label{eq:w1}{w_{1}=\frac{w_{2}}{4\pi{r}}}\end{equation}
\begin{equation}\label{eq:w0}{w_{0}=\frac{w_{2}}{4\pi{r}^2}}\end{equation}
The weight functions $w_{2}$ and $w_{3}$ have the relation
\begin{equation}\label{w2_w3_relation}{w_{3}=\int_{r}^{\infty}{w_{2}(\vec{r})dr}\mbox{~~~~or equivilantly,~~~~}-\frac{\partial{w_3(r)}}{\partial{r}}=w_2(r)}\end{equation}
which will be important to keep in tact when moving to SFMT~\cite{schmidt1999density}.

The weight functions can be related to the Mayer function 
\begin{align}
     f(r)=\exp^{-\frac{V(r)}{k_{B}T}}-1
\end{align} 
where r is the distance between the centers of two hard spheres, and 
$V(r)$ is the interatomic potential between two hard spheres given by 
\begin{align}
    V(r)=\left\{ \begin{array}{rc} \infty & 0<r \leq 2R \\ 0  & r>2R \end{array}\right.
\end{align}
Evaluating Equation with $V(r)$ given by Equation,  
the Mayer function for a hard-sphere fluid is found to be
\begin{equation}\label{f(r)step}{f(r)=-\Theta(|\vec{r}|-2R)}\end{equation} 
which can be written in terms of the weight functions if two 
additional vector weight functions $\vec{w_2}$ and $\vec{w_1}$ are introduced
\begin{equation}\label{eq:w_v2}{\vec{w_{2}}=w_{2}\frac{\vec{r}}{r}}\end{equation}
\begin{equation}\label{eq:w_v1}{\vec{w_{1}}=w_{1}\frac{\vec{r}}{r}}\end{equation} 
The Mayer function can then be written in terms of the weight functions~\cite{Hansen}
\begin{equation}\label{mayer_deconvolution}{f(r)=-\Theta(|\vec{r}|-2R)= -2(w_3 \otimes w_0 + w_2 \otimes w_1 + \vec{w_2} \otimes \vec{w_1})}\end{equation}

>>>>

\textcolor{red}{FROM HERE}
%\begin{equation}{\Theta(|\vec{r}|-R)=\left\{ \begin{array}{rc} 1 & 0<r \leq R \\ 0  & r>R \end{array}\right.}\end{equation}

@@

given by

@@

%This can easily be shown by putting the interatomic potential between two hard spheres
%given by 
    %V(r)=\left\{ \begin{array}{rc} \infty & 0<r \leq 2R \\ 0  & r>2R \end{array}\right.
%into the equation for the Mayer function
     %f(r)=\exp^{-\frac{V(r)}{k_{B}T}}-1

@@

                 &+ \color{white}\left[\color{black}\left(\int n\delta(r-R) d\vec r\right)\left(\int n\frac{\delta(r-R)}{4\pi R} d\vec r \right) \right]\color{black}V   \\          

@@

which are needed for the relation to be satisfied, 

@@

                &+ \color{white}\left(\color{black}\int w_1(\vec u - \vec r_i)w_2(\vec u - \vec r_j) d\vec x ~-\int \vec {w}_1(\vec u - \vec r_i)\cdot\vec {w}_2(\vec u - \vec r_j) d\vec u\right)    \\

@@

                &+ \color{white}\left[\color{black} \int n(\vec r_i) \vec {w}_1(\vec u - \vec r_i)~d\vec r_i \cdot \int n(\vec r_j) \vec {w}_2(\vec u - \vec r_j)~d\vec r_j \right]\color{black}d\vec u  \\

@@

                %&\text{or replacing u notation with r} \nonumber \\
                &= k_BT\int \Phi(n(\vec r))~d\vec r             

@@

    n_\alpha(\vec u)=\int n(\vec r')w_\alpha(\vec u-\vec r')~d\vec r'  

@@

Lifting the restriction to the low density limit, Rosenfeld derived an
expression for the excess Helmholtz free energy by noting that the higher
order terms in the virial expansion can all be written in terms of an 
"exclusion volume" which is given by Equation~\ref{exclusion-volume}, 
and an "overlap volume".
The exclusion volume is the spherical volume about the center of one sphere 
which the center of another sphere can not enter, and is used to describe
terms with $f_{ij}=f(|\vec r_i - \vec r_j|)$ as has been seen. The overlap volume is 
the volume of intersection between two spheres that overlap, and is used in conjunction 
with the exclusion volume to describe higher order terms in the expansion~\cite{rosenfeld1988}. 
%
The resulting expression for the excess Helmholtz free energy with an 
updated version of $\Phi_3$ that was later constructed by Tarazona is given by
\begin{align}
    F_{excess}[n(\vec{r})] &= k_BT\int(\Phi_1(\vec{r})+\Phi_2(\vec{r})+\Phi_3(\vec{r}{)) d}\vec{r} \\
    %\Phi_1 &= -n_{0}ln(1-n_{3})  \\
    %\Phi_2 &= \frac{n_{1}n_{2}}{1-n_{3}} \\
    %\Phi_3 &= \frac{n_{2}^3}{24\pi(1-n_{3})^2}
    \Phi_1 &= -n_{0}\ln(1-n_{3}) \\
    \Phi_2 &= \frac{n_{1}n_{2}-\vec{n_{1}}\cdot\vec{n_{2}}}{1-n_{3}} \\
    \Phi_3 &= \frac{{n_2}^3-3n_2\vec{n}_{v2}\cdot\vec{n}_{v2}+\frac{9}{2}[\vec{n}_{v2}\cdot{\overleftrightarrow{n}_{m2}}\cdot{\vec{n}_{v2}}-\operatorname{Tr}({\overleftrightarrow{n}^3_{m2}})]}{24\pi(1-n_3)^2}  
\end{align}
where in addition to the weight functions already defined, a tensor weight function is given by
\begin{align}\label{eq:tensorweight-methods}
     \overleftrightarrow{w}_{m2}(\vec{r}) = w_2(r)\left(\frac{\vec{r}\vec{r}}{r^2}-\frac{I}{3}\right) 
\end{align}
The weighted densities $n_0, n_1, n_2, n_3, \vec{n}_1, \vec{n}_2$ and $\overleftrightarrow{n}_{m2}$
all depend on the spatially varying number density profile $n(\vec r)$.
\begin{align}%\label{eq:numdenprofile}
	n_\alpha(\vec{r})=\int_{Volume}{n(\vec{r'})w_\alpha(\vec{r}-\vec{r'})d{\vec{r'}}}
\end{align}
This result reduces to same result obtained from Scaled Particle Theory 
for a homogeneous hard-sphere fluid.

The FMT equations shown so far have been for a hard-sphere fluid~\cite{Hansen}.
All of the weight functions can be expressed in terms of 
$w_{2}(r)$ which, for a hard-sphere fluid, consists of a delta function.
The weight function $w_{2}(r)$ is in turn related to $w_{3}(r)$ through 
the relation
\begin{align}\label{w2_w3_relation}
    w_{3}=\int_{r}^{\infty}{w_{2}(\vec{r})dr}\mbox{~~~~or equivilantly,~~~~}-\frac{\partial{w_3(r)}}{\partial{r}}=w_2(r)
\end{align}
%which will be important to keep in tact when moving to SFMT~\cite{schmidt1999density}.
Taking the derivative of the Mayer function in Eq~\ref{f(r)step} provides 
another important relation expressed in terms of $w_{2}(r)$ 
%that will be important 
%to keep in tact when moving to SFMT~\cite{schmidt2000fluid}.
\begin{align}\label{mayerder=w2convolution}
     \frac{df(r)}{dr} = w_2 \otimes w_2 = \int{w_2(r')w_2(r-r')dr'}
\end{align} 
Soft Fundamental Measure Theory extends FMT to fluids 
with soft potentials by keeping the relationships between the weight 
functions, and the equation for the derivative of the Mayer function 
the same, 
but replacing $w_{3}(r)$ with a weight function appropriate 
for a soft-sphere potential~\cite{schmidt1999density, schmidt2000fluid}. 
This is what we do in forming a functional for the Weeks-Chandler-Anderson 
fluid as detailed in the next chapter on Methods.

%\textcolor{red}{TO HERE ----------------------------------}
%
%In order to apply classical Density Functional Theory to a system that has
%a fixed temperature, volume, and number of particles, a functional for 
%the Helmholtz free energy must first be formed. An expression for the ideal 
%portion of the Helmholtz free energy is given by Equation~\ref{eq:Fideal-n(r)}, 
%but forming an expression for the excess Helmholtz free
%energy from Equation~\ref{eq:Fexcess-simplified} for the particular fluid 
%being modeled can be challenging. 
%Soft Fundamental Measure Theory (SFMT) is a method for forming an 
%expression for the excess Helmholtz free energy of a soft-sphere fluid
%that does not depend on explicitly taking into account the interaction 
%that each sphere with every other sphere in the fluid (as required by 
%Equation~\ref{eq:Fexcess-simplified}). In the next chapter on methods, we
%will use an SFMT functional that we adapt to fit the soft-sphere WCA fluid.
%SFMT was developed by Schmidt~\cite{schmidt1999density, schmidt2000fluid} 
%for soft-spheres. It is an extension of Fundamental Measure Theory (FMT) 
%originally developed by 
%Rosenfeld~\cite{rosenfeld1989, rosenfeld1994, rosenfeld1996, fmtfromsptandsignerror} 
%for the hard-sphere fluid, and which expanded 
%Scaled Particle Theory (SPT)~\cite{santos2012phi3} 
%to inhomogeneous, or non-uniform hard-sphere fluids.

%\textcolor{red}{BEGIN COMMENTED OUT SECTION...} %########################

%Scaled Particle Theory
%seeks a general expression for the excess chemical 
%potential of a homogeneous hard-sphere fluid which can then be integrated 
%to find the excess Helmholtz free energy according to the relation
%\begin{equation}\mu_{ex}=\frac{\partial{F_{ex}}}{\partial{N}}\bigg|_{T,V}{~~~~~}\rightarrow{~~~~~}F_{ex}=\int{\mu_{ex}dN}\end{equation}
%It is an extension of the work done by Widom who showed that the excess 
%chemical potential of a homogeneous fluid corresponds to the reversible 
%work of inserting a sphere of radius R into a fluid consisting of hard 
%spheres of radius R. 
%\begin{align}
	%\mu_{ex}=W_{rev}(R){~~~~}\text{work to insert a hard sphere of radius R}
%\end{align}
%Widom's result was obtained by considering the difference 
%in the excess Helmholtz free energy when one atom is added to an otherwise 
%closed system. He showed that the excess chemical potential is related to 
%the ensemble average of the Boltzman factor for the potential energy 
%difference $V_{diff}$ between a system with N atoms and one with N+1 atoms. 
%The resulting equation, shown below, is known as Widom's Insertion 
%Formula~\cite{Hansen}.
%\begin{align} \label{mu-der-int}
    %\mu_{ex}=\frac{F_{ex}(N+1)-F_{ex}(N)}{\Delta{N}}\bigg|_{T,V}
%\end{align}
%\begin{equation}\label{widoms-insertion-formula}{~}=-k_BT\ln\left(<e^{-\beta{V_{diff}}}>\right)\end{equation}
%where 
%\begin{align}
    %<e^{-\beta{V_{diff}}}>=\sum_s{P_se^{-\beta V_s}}
%\end{align}
%and
%\begin{align}
    %Z=\sum_s{e^{-\beta V_s}}
%\end{align}

%The quantity $<e^{-\beta{V_{diff}}}>$ can be evaluated by considering that
%there will be a change in the potential energy of $V_{diff}$ if one sphere
%is added, but no change in potential energy if no sphere is added ($V_{diff}=0$). 
%In this case, $P_s=\frac{e^{-\beta V_s}}{Z}$.
%%at each point in the fluid, there is a probability that 
%%a hard sphere of radius R has space available to exist at that point
%%without overlapping with other spheres, or it does not, as shown in 
%Widom's Insertion formula Equation~\ref{widoms-insertion-formula}, 
%then becomes~\cite{Hansen}
%\begin{align} 
	%\mu_{ex} &= -k_BT\ln\left(e^{-\beta{V_{diff}}}+1\right)  \\
	         %&= V_{diff} \\
             %&= W_{rev}(R)  \label{workrev}
%\end{align}
%\begin{figure}
    %\centering
    %\includegraphics[height=7cm]{figs/P_overlap.pdf}
    %\caption{No energy is needed to place a sphere at a position where 
    %there is no overlap, such as that shown by the black dot near the 
    %top. But it is not possible to place a sphere at a position where 
    %an overlap occurs.}
    %\label{fig:p_overlap}
  %\end{figure}
%The quantity $<e^{-\beta{V_{diff}}}>$ can also be evaluated by considering
%that it takes no energy for a hard sphere to be placed at a point
%in the fluid where it does not overlap with any other spheres 
%($V_{diff}=0$), but it would require infinite energy ($V_{diff}=\infty$)
%to place a sphere where it would overlap another sphere, as described 
%in Figure~\ref{fig:p_overlap}. 
%In this case Equation~\ref{widoms-insertion-formula} becomes~\cite{Hansen}
%\begin{align} \label{muexcess}
  %\mu_{excess}(R_{cavity}=R)=-k_BT\ln(1-n\frac{4\pi}{3}R^3) 
%\end{align}
%where the radius of the cavity $R_{cavity}$ equals the radius of a 
%hard sphere R, and $nV_{Sphere}$, which is equal to the total volume 
%occupied by the spheres divided by the total volume available, 
%is the probability that a sphere cannot be placed at some random
%point in the homogeneous fluid of number density, $n$, without
%overlapping with another sphere. $P_s$ would then have values of
%$nV_{Sphere}$ and $1-nV_{Sphere}$.
%Combining  Equations~\ref{workrev} 
%and \ref{muexcess} gives
%\begin{align}
  %%W_{rev}(R_{cavity}=R)=-k_BT\ln(1-n\frac{4\pi}{3}R^3)
  %W_{rev}(R_{cavity}=R)=-k_BT\ln(1-\eta) 
%\end{align}
%where $\eta$ is the packing fraction defined as
%\begin{equation}{\eta = \frac{\mbox{Volume occupied by the spheres}}{\mbox{Total Volume}}}\end{equation}
%\begin{equation}{\eta = \frac{N\frac{4}{3}\pi{R^3}}{V}}\end{equation}

%Scaled Particle Theory forms a more general result for the reversible work 
%as a function of the radius of the cavity by considering additional 
%cases where the cavity is larger, and much larger than the radius of 
%a hard sphere, and requiring continuity of the functions for the 
%different cases and their derivatives (first and second). 
%By setting the radius of the cavity to the hard sphere radius, the 
%more general work equation becomes equal to the chemical potential. 
%Details of this procedure can be found 
%in Theory of Simple Fluids by Hansen and McDonald~\cite{Hansen}.  
%An expression for the excess Helmholtz free energy in terms of the
%packing fraction $\eta$ can then be obtained through 
%Equation~\ref{mu-der-int}.

%%By requiring continuity of the functions valid for different cavity 
%%sizes, along with their first and second derivatives, an equation for 
%%the work is obtained which can then be used to form 
%%set equal to the excess chemical 
%%potential by setting the cavity radius to the radius of hard sphere. 
%%
%%Forming a more general result by requiring continuity of the functions, 
%%along with their first and second derivatives, for the reversible work
%%written for fluids with a cavity radius equal to, larger than, or very 
%%much larger than the hard sphere radius R, 
%%
%%Scaled Particle Theory arrives at 
%%an expression for the excess Helmholtz free energy of 
%%a homogeneous hard-sphere fluid in terms of the packing fraction $\eta$.
%%For details, see Theory of Simple Fluids by Hansen and McDonald~\cite{Hansen}. 
%\begin{align}\label{Fexcess-SPT}
    %F_{excess}=k_BT\left(-ln(1-\eta)+\frac{3\eta}{1-\eta}+\frac{3{\eta}^2}{2(1-\eta)^2}\right)N
%\end{align}

%Fundamental Measure Theory can be constructed from Equation~\ref{Fexcess-SPT}  
%%and provides an expression for the excess Helmholtz free energy of an 
%%inhomogeneous 
%%hard-sphere fluid as a functional of the number density profile $n(\vec r)$. 
%%
%%Soft Fundamental Measure Theory (SFMT), which will be used in this paper, 
%%is an extension of FMT and provides an expression for the excess Helmholtz
%%free energy of fluids with soft potentials like that of the WCA fluid. 
%%It will be helpful to continue looking at FMT before addressing SFMT.
%%FMT begins 
%by noticing that a quantity $G_{3}$ can be defined such that
%\begin{equation}{\eta =\left(\frac{N}{V}\right)\frac{4}{3}\pi{R^3}=nG_{3}}\end{equation}
%where $G_{3}$ is the volume of a sphere. 
%Likewise, by defining quantities
%\begin{equation}{G_{2}=4\pi{R^2}}\end{equation}
%\begin{equation}{G_{1}=R}\end{equation}
%\begin{equation}{G_{0}=1}\end{equation}
%where $G_{2}$ is the surface area of a sphere, and $G_{1}$ is the 
%radius of a sphere, Equation~\ref{Fexcess-SPT} can be written as
%\begin{equation}\label{FexfromSPTinthermsofG}{F_{excess}=k_{B}T\left(-nG_{0}ln(1-nG_{3})+\frac{nG_{1}nG_{2}}{1-nG_{3}}+\frac{nG_{2}^3}{24\pi(1-Gn_{3})^2}\right)V}\end{equation}
%The quantities $G_{3}, G_{2}, G_{1},$ and $G_{0}$ are fundamental 
%geometric measures of a sphere, and are what give rise to the name
%Fundamental Measure Theory. Introducing a set of variables
%%weighted densities $n_{i}=nG_{i}$ 
%given by
%\begin{equation}\label{n3}{n_{3}=nG_{3}=\left(\frac{N}{V}\right)\frac{4}{3}\pi{R^3}=\eta}\end{equation}
%\begin{equation}\label{n2}{n_{2}=nG_{2}=\left(\frac{N}{V}\right)4\pi{R^2}=\frac{3\eta}{R}}\end{equation}
%\begin{equation}\label{n1}{n_{1}=nG_{1}=\left(\frac{N}{V}\right)R}\end{equation}
%\begin{equation}\label{n0}{n_{0}=nG_{0}=\left(\frac{N}{V}\right)}\end{equation}
%Equation~\ref{FexfromSPTinthermsofG} can be written as
%\begin{align}\label{FexfromSPT}
    %F_{excess}=k_{B}T\left(-n_{0}ln(1-n_{3})+\frac{n_{1}n_{2}}{1-n_{3}}+\frac{n_{2}^3}{24\pi(1-n_{3})^2}\right)V
%\end{align}
%which has the form 
%\begin{align}
    %F_{excess} = k_BT(\Phi_1+\Phi_2+\Phi_3)V
%\end{align}
%%where 
%\begin{align}
   %\Phi_1 &= -n_{0}\ln(1-n_{3}) \label{Phi1equation} \\
   %\Phi_2 &= \frac{n_{1}n_{2}}{1-n_{3}} \\
   %\Phi_3 &= \frac{n_{2}^3}{24\pi(1-n_{3})^2}   \label{oldPhi3equation}
%\end{align}
